\clearpage{\thispagestyle{empty}}
\section{Representations of finite groups}

\marginnote{Include note on source!} 

\paragraph{First definitions.}

The main purpose of this text is to study linear representations of finite groups.

Let $G$ be a finite group written multiplicatively. Denote its order by $|G|$ and the action of its elements with $\cdot$, eg. $g \cdot x$.

Let $V$ be a finite-dimensional vector space over the field of complex numbers $\CC$. Its group of automorphisms is denoted by $\GL(V)$. If $V$ is provided with a basis, usually denoted $(\bas_i)_{i=1}^n$, where $n = \dim V$, then $\GL(V)$ is identified with the set of linear transformations of $V$, denoted $\GL_n(\CC)$\cite[18.1]{DummitFoote}.

\begin{definition}[Representation]\cite{Serre}
	Given a finite group $G$, a representation of $G$ in the vector space $V$ is a homomorphism
	\begin{align}\label{eq:DefRepr}
		\rho: G \rightarrow \GL(V).
	\end{align}
\end{definition}
For every $g$ in $G$, there is a linear map $\rho_g$ in $\GL(V)$ with an action on the elements of $V$ defined by 
\begin{align*}
	g \cdot \vvec = \rho_g (\vvec).
\end{align*}
The linearity of the map means that for any $\vvec, \wvec \in V$,
\begin{align}\label{eq:linearityOfg}
	g \cdot (a\vvec + b\wvec) = ag\cdot\vvec + bg\cdot\wvec,
\end{align} 
and also since it is a homomorphism, for any $g,h \in G$ we have
\begin{align}\label{eq:homomorphism}
	\rho_{gh} = \rho_g \rho_h.
\end{align}
From the homomorphism of $\rho$, two consequences follow.
\begin{proposition}
	For the identity element $e$ of $G$ and an arbitrary element $g$ with inverse $g^{-1}$ in $G$ we have,
	\begin{align}\label{eq:rhoIdAndInv}
		\rho_e = \id \quad \text{and} \quad \rho_g^{-1} = \rho_{g^{-1}},
	\end{align}
	where $\id$ is the identity transformation and $\rho_{g^{-1}}$ is the inverse of the representation of $g$.
\end{proposition}
\begin{proof}
	Take $g$ as an arbitrary element of $G$. The first identity follows from taking $h=e$ in Equation~\ref{eq:homomorphism}:
	\begin{align*}
		\rho_{eg} = \rho_e \rho_g.
		%\rho(eg) = \rho(e)\rho(g). %	\rho(g) \overset{!}{=} \rho(eg) = \rho(e)\rho(g)
	\end{align*}
	Since $eg=g$ for any $g\in G$ we must have that $\rho_g = \rho_e\rho_g$ which is true if and only if $\rho_e = \id$. Instead taking $h=g^{-1}$ we have:
	\begin{align*}
		\rho_{gg^{-1}} = \rho_g \rho_{g^{-1}},
		%\rho(g) \rho(g^{-1}) =  \rho(gg^{-1}~). %\overset{!}{=} \rho(e) = \id.
	\end{align*}
	but $gg^{-1} = e$ and $\rho_e = \id$, implying $\rho_{g^{-1}} = \rho_g^{-1}$.
\end{proof}

\begin{note}
	A vector space $V$ together with a group action fulfilling Equations \ref{eq:DefRepr}, \ref{eq:homomorphism} and \ref{eq:rhoIdAndInv} gives $V$ the structure of a $G$-module \cite[1.3]{Sagan}. To avoid a treatment on modules, if a vector space $V$ is a $G$-module it will be referred to as a \textit{representation space} of $G$.
\end{note}

\begin{note}
	The homomorphism $\rho$, the set of maps $\{\rho_g\}_{g \in G}$ and the representation space $V$ are interchangeably and abusively called the \textit{representation of $G$}.
\end{note}

\paragraph{Choice of basis.} 

If a basis $\{\bas_i\}_{i=1}^n$ is provided for a representation space, then a \textit{matrix representation} can be provided. In this case, $\rho_g$ is the matrix in $\GL_n(\CC)$ associated with the action of $g$ expressed in the basis provided. A matrix representation is not canonical and is dependent on the basis chosen.

\paragraph{Degree of a representation.} 

\begin{definition}[Degree of a representation]
	Let $V$ be a representation space of $G$. Then the dimension of $V$ is referred to as the degree of the representation.
\end{definition}	